---
title: "ABTesting Project"
output:
  html_document:
    toc: false
    toc_float: false
    theme: spacelab
---

 
Data Cleaning
```{r}
# Removing uninformative Columns/Rows
data <- read.csv("/Users/77wu/Desktop/data.csv")

df <- data[, !(names(data) %in% c("IPAddress","Progress","Duration..in.seconds.","Finished","RecordedDate","StartDate","EndDate","Status","ResponseId","RecipientLastName","RecipientFirstName","RecipientEmail","ExternalReference","LocationLatitude","LocationLongitude","DistributionChannel","UserLanguage","Q1","Q_UnansweredPercentage","Q_UnansweredQuestions"))]
df <- df[-(1:2), ]
df$Q8Control[df$Q8Control == "Maybe"] <- "No"
head(data)
```
```{r}
library(dplyr)

colnames(df)[1] <- "Gender"
colnames(df)[2] <- "Frequency"
colnames(df)[3] <- "AccOrGuest"
colnames(df)[4] <- "SignupLikelihood"
colnames(df)[5] <- "PrivacyConcern"
colnames(df)[6] <- "PopupWindow"
colnames(df)[7] <- "Control"
colnames(df)[8] <- "Treatment"
colnames(df)[9] <- "WhyNot"
colnames(df)[10] <- "WhyNotText"
colnames(df)[11] <- "AppropriateTiming"
colnames(df)[12] <- "Credibility"
colnames(df)[13] <- "FurtherExploration"
colnames(df)[14] <- "WhichCondition"
df$WhichCondition[df$WhichCondition == "immediately on the landing page."] <- "Immediately"
df$WhichCondition[df$WhichCondition == "after some kind of user interactions (ex: clicked on a product, clicked on a tab.....)"] <- "Interactions"
df <- df %>%
  mutate(Group = if_else(Treatment %in% c("Yes", "No"), "Treatment", "Control"))

df <- df %>%
  mutate(
    YESNO = case_when(
      Control %in% c("Yes", "No") ~ Control,
      Treatment %in% c("Yes", "No") ~ Treatment,
      TRUE ~ NA_character_ # Use this line to handle rows where neither column has "Yes" or "No"
    )
  )
df <- df[, !(names(df) %in% c("WhyNotText","Control","Treatment"))]
head(df)
```
```{r}
# User Background
library(ggplot2)

df_summary <- df %>%
  group_by(SignupLikelihood, PrivacyConcern, Gender) %>%
  summarize(Count = n(), .groups = 'drop')

ggplot(df_summary, aes(x = SignupLikelihood, y = PrivacyConcern, color = Gender, size = Count)) +
  geom_point(alpha = 0.7, show.legend = TRUE) +  # Remove the size legend if it's not needed
  labs(title = "Signup Likelihood vs. Privacy Concern by Gender",
       x = "Signup Likelihood",
       y = "Privacy Concern") +
  scale_color_brewer(palette = "Pastel1") +
  scale_size(range = c(4, 11)) +  # Adjust the range of sizes here
  theme_minimal()


```
Our analysis of the sample data indicates a lack of a clear trend between signup likelihood and privacy concern among users. Despite varying levels of signup likelihood, privacy concerns among users are diverse, suggesting that the decision to sign up is influenced by factors beyond privacy considerations alone. 

Also, our sample reveals a higher proportion of female users, who demonstrate a greater tendency to sign up for an account on the retail website where they have made purchases. 
```{r}
#split control and treatment data
control <- df[df$Group == "Control", ]
treatment <- df[df$Group == "Treatment", ]
control$WhyNot[control$YESNO == "Yes"] <- NA
treatment$WhyNot[treatment$YESNO == "Yes"] <- NA

```
```{r}
# Create tables of counts for the Control and Treatment columns
control_counts <- table(control$YESNO)
treat_counts <- table(treatment$YESNO)

# Set up the plotting area to have 1 row and 2 columns
par(mfrow = c(1, 2))

# Plot the pie chart for Control
pie(control_counts, 
    labels = names(control_counts), 
    main = "Sign up Pie Chart of Control")

# Plot the pie chart for Treatment
pie(treat_counts, 
    labels = names(treat_counts), 
    main = "Sign up Pie Chart of Treatment")

par(mfrow = c(1, 1))

```
```{r}
# t-test b/w different factors of control and treatment groups
# AppropriateTiming => How well does the user satisfy with the given popup timing
control_satisfaction <- as.numeric(control$AppropriateTiming)
treatment_satisfaction <- as.numeric(treatment$AppropriateTiming)
t_test_satisfaction <- t.test(control_satisfaction, treatment_satisfaction)
t_test_satisfaction

# Credibility => How the user think the given popup timing affect the website credibility
control_credibility <- as.numeric(control$Credibility)
treatment_credibility <- as.numeric(treatment$Credibility)
t_test_credibility <- t.test(control_credibility, treatment_credibility)
t_test_credibility

#FurtherExploration => How willing the user would like to keep exploring the website after the given popup 
control_FurtherExploration <- as.numeric(control$FurtherExploration)
treatment_FurtherExploration <- as.numeric(treatment$FurtherExploration)
t_test_FurtherExploration <- t.test(control_FurtherExploration, treatment_FurtherExploration)
t_test_FurtherExploration
```

```{r}
#Analyze WhyNot column

whyNotValues <- control$WhyNot
# Split the strings by comma
splitValues <- strsplit(whyNotValues, split = ",", fixed = TRUE)
# Flatten the list into a single vector
flatValues <- unlist(splitValues)
valueCounts <- table(flatValues)
control_countsDf <- as.data.frame(valueCounts)
names(control_countsDf) <- c("Reason", "Frequency")
control_countsDf

whyNotValues <- treatment$WhyNot
# Split the strings by comma
splitValues <- strsplit(whyNotValues, split = ",", fixed = TRUE)
# Flatten the list into a single vector
flatValues <- unlist(splitValues)
valueCounts <- table(flatValues)
treat_countsDf <- as.data.frame(valueCounts)
names(treat_countsDf) <- c("Reason", "Frequency")
treat_countsDf
```
```{r}
treat_countsDf$Group <- 'Treatment'
control_countsDf$Group <- 'Control'
combinedDf <- rbind(treat_countsDf, control_countsDf)

ggplot(combinedDf, aes(x = Reason, y = Frequency, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "Frequency of Reasons by Group",
       x = "Reason",
       y = "Frequency") +
  scale_fill_manual(values = c("Treatment" = "lightblue", "Control" = "pink")) 

```

```{r}
library(dplyr)
df_summary <- df %>%
  group_by(AccOrGuest, YESNO, Group) %>%
  summarize(Count = n(), .groups = 'drop')

ggplot(df_summary, aes(x = AccOrGuest, y = YESNO, color = Group, size = Count)) +
  geom_point(alpha = 0.5, position = position_jitter(width = 0.1, height = 0)) +
  geom_text(aes(label = Count), position = position_jitter(width = 0.1, height = 0), vjust = -0.5) +
  scale_size_continuous(range = c(3, 10)) + # Adjust size range as needed
  labs(title = "Dot Plot of Sign up Response by Account or Guest Status",
       x = "Account or Guest",
       y = "Whether or not to Sign up") +
  scale_color_manual(values = c("Control" = "lightblue", "Treatment" = "pink")) +
  theme_minimal() +
  guides(size = FALSE) # Hide the size legend



```
```{r}
filtered_values <- df %>%
  filter(AccOrGuest == "Create an account", YESNO == "No", Group == "Treatment") %>%
  select(WhichCondition)

# Display the filtered values
print(filtered_values)

```


```{r}
filtered_values <- df %>%
  filter(AccOrGuest == "Create an account", YESNO == "No", Group == "Treatment") %>%
  select(WhyNot)

print(filtered_values)
```
```{r}
```
```{r}
```
```{r}
```
```{r}
```
